The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-07-29 brainscopycut.tex
cite software colophon

>>>>

\begin{new}

\subsection*{Software colophon}

Finally, this paper was developed using Python's scientific computing ecosystem~\citep{millman_python_2011}.
In particular, we directly used NumPy and SciPy~\citep{walt_numpy_2011}, Matplotlib~\citep{hunter_matplotlib:_2007}, Pandas~\citep{mckinney_data_2010}, scikit-learn~\citep{pedregosa_scikit-learn:_2011}, NetworkX~\citep{hagberg_exploring_2008}, NLTK~\citep{bird_nltk_2009}, IPython~\citep{perez_ipython:_2007}, and many other libraries from the Python ecosystem.
The software and analyses written for the paper are documented and published under a Free Software license.
They can be found at \url{https://github.com/wehlutyk/brainscopypaste}.

\end{new}
